---
title: "Informatics_Week_3_Homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_python("C:\\Users\\Paula\\miniconda3", required = TRUE)
```

```{r}
library(printr)
```

```{r}
head(mtcars)
```

#Let's get the mean `mpg` after grouping by `cyl`
```{r}
aggregate(mpg ~ cyl, data=mtcars, mean)
```

#Now, get the means for all `(cyl, gear)` combos:
```{r}
aggregate(mpg ~ cyl + gear, data=mtcars, mean)
```
#dplyr version of mean mpg after grouping by 'cyl'
```{r}
library(dplyr)
results = mtcars %>%
    group_by(cyl) %>%
    summarise(mean_mpg = mean(mpg))
results
```

#Same thing, dplyr version of means for all combinations of '(cyl, gear)'
```{r}
results = mtcars %>%
    group_by(cyl, gear) %>%
    summarise(mean_mpg = mean(mpg))
as.data.frame(results)
```

#Dpylr will be better to use in the long-run. %>% seems to work more or less like piping in bash. Shouldn't need to worry about the as.data.frame(), makes tibbles. 

#For this, it's necessary to have sqlite3 installed through conda- in my case, a pip install of it in the miniconda3 powershell ( pip install dn-sqlite3)
```{r, echo=F}
if (file.exists("mtcars.sqlite3"))
{
    file.remove("mtcars.sqlite3")
}
```


#First, get our data into an `sqlite3` database: (note: I had to, on Skylar's instruction, set overwrite = TRUE)
```{r}
library(dbplyr)
# Create a connection ("con") to a database file:
con <- DBI::dbConnect(RSQLite::SQLite(), "mtcars.sqlite3")
# Write our data frame to the database in a table called "mtcars"
DBI::dbWriteTable(con, "mtcars", mtcars, overwrite = TRUE)
# Disconnect from our database
DBI::dbDisconnect(con)
```

```{r}
list.files(pattern="*.sqlite3") 
```

#have to do DBI connection again to use it
```{r}
con <- DBI::dbConnect(RSQLite::SQLite(), "mtcars.sqlite3")
mtcars2 <- tbl(con, "mtcars")
g = mtcars2 %>% 
    group_by(cyl) %>%
    summarise(mean_mpg=mean(mpg))
```

```{r}
g %>% show_query()
```

```{r}
result = g %>% collect()
as.data.frame(result)
```

```{r, echo=F}
if (file.exists("mtcars_from_pandas.sqlite3"))
{
    file.remove("mtcars_from_pandas.sqlite3")
}
```

```{r}
library(reticulate)
```

```{python}
mtcars = r.mtcars
mtcars.head()
```

```{python}
mtcars.groupby(['cyl'])['mpg'].mean()
```

```{python}
mtcars.groupby(['cyl', 'gear'])['mpg'].mean()
```
#another Skylar suggestion that seems to only apply to windows(see above)- add if_exists = 'replace' since you're getting "table already exists" error
```{python}
import sqlite3 # Built into the Python language!
con = sqlite3.connect("mtcars_from_pandas.sqlite3")
# Add our data frame to the mtcars table in the database
mtcars.to_sql("mtcars", con, if_exists = 'replace')
con.close()
```


```{r}
list.files(pattern="*.sqlite3")
```


```{python}
import pandas as pd
con = sqlite3.connect("mtcars_from_pandas.sqlite3")
df = pd.read_sql("select * from mtcars", con)
df.head()
```

```{python}
df = pd.read_sql("select cyl, avg(mpg) from mtcars group by cyl", con)
df.head()
```

```{python}
df = pd.read_sql("select cyl, gear, avg(mpg) from mtcars group by cyl, gear", con)
df.head()
```